\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-08-12 doc/sw-system.tex

\subsubsection{Instant Feedback}

@@

\question{PJM}{Does the feedback lead to volunteers leaving the site more 
quickly, or less quickly? Does negative feedback have more impact than
positive?}

@@

\subsection{Stage 1: Initial Classification}
\label{sec:design:stage1}

Interface fast due to pre-loading of images, and minimizing interaction.
Trade-off between speed and accuracy. Decreasing training rate.

Quick dashboard provides simple ways to explore further: zoom, contrast
controls.

Spotting lenses: Markers to be placed. Two reasons: first, to give good
feedback. Second, to focus attention.

Non-lenses marked? Favourite button instead, enabling serendipitous
discovery of other interesting things, separate from lenses.

Retirement of low probability systems. Concentrates sample, provides more
``bacon'' (while slightly skewing "sim frequency"). Note that this feature
means that everyone contributes to detection of lenses: luck is made for the
few that happen to see the new lenses, by the masses that did the rejection.
Group effort.

Sims vs duds leads to inclusive search -- click on anything you think etc...

\subsection{Stage 2: Refinement}
\label{sec:design:stage2}

Goal: assess candidates, reject false positives by comparing with training set
of non-obvious non-lenses. Produce a sample rankable by probability.

Reconfigured website: more detailed SG, more detailed feedback. Orange
background to make it obvious stage 2 is different. Slower image presentation.
Higher, constant training rate.

@@

>>>>

\subsubsection{Training Subjects and Instant Feedback}

@@

@@

\subsection{Staged Classification}
\label{sec:design:stages}

We now describe briefly the two-stage strategy that was employed in the CFHTLS
project, initial classification (involving the rejection of very large numbers
of non-lenses), and refinement (to further narrow down the sample). The web
application was reconfigured between the two stages, to assist in their
functioning.

\subsubsection{Stage 1: Initial Classification}

The goal of a stage 1 classification is to achieve a high rejection rate,
while maintaining high completeness.  In this mode, therefore, the pre-loading
of images was used to make the sliding in of new subjects happen quickly, to
provide a sense of urgency: initial classification must be done fairly
quickly for the search to be completed within a reasonable time period.  We
expect some trade-off between speed and accuracy, which we return to in the
results section below. Completion of the search requires subjects to be
``retired'' over time, as a result of their being classified. We do this by
analyzing the classifications on a daily basis, as described in
\Sref{sec:swap} below. As subjects are retired, new ones are ingested into
the web app for classification. This means that the discovery of lens
candidates in stage 1 is truly a community effort: to detect a lens candidate,
many non-lenses must first be rejected.

The stage 1 training set was chosen to be quite clear cut, in order to err on
the side of inclusivity, and so ensure high completeness. For the training
duds we selected several hundred images at random, and three of us (AV, AM,
PM) inspected them and discarded anything that could be a lens candidate. The
remainder were ingested into the site.

\subsubsection{Stage 2: Refinement}

At stage 2, the goal is to define a final sample that has both high
completeness and high purity. To this end, a more demanding training set was
defined, where the duds all contain an object identified by one of us (AV, AM
and PM) as a potential false positive. \Fref{fig:training:gallery} shows some
example images from the CFHTLS stage 2 training set.

\todo{Phil}{Show some example sims and duds...}

We also attempted to encourage discernment by changing the look and feel of
the app, slowing down the arrival of new images, and switching the background
color to bright orange to make it clear that a different task was being set.
The frequency with which training images were shown was fixed at 1 in 3.
Finally, the Spotter's Guide was upgraded to include more detailed discussion
of various possible false positives.

@@

\todo{Phil,Chris}{Write about offline analysis here (issue \#40)}
